---
title: "Replication Project Code"
author: "Tysen Dauer"
date: "11/19/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Script for ANCOVA
Start with this resource for R ANCOA code: https://www.statmethods.net/stats/anova.html.

And this is my working reference for understanding ANCOVA: http://proquest.safaribooksonline.com/book/statistics/9781449361129/7dot-the-pearson-correlation-coefficient/exercises_id11_html#X2ludGVybmFsX0h0bWxWaWV3P3htbGlkPTk3ODE0NDkzNjExMjklMkZhbmNvdmFfaHRtbCZxdWVyeT10JTIwdGVzdA==.

Here is some fake data to test this out.
```{r}
fakeData <- read.csv(file="~/Desktop/fakeData.csv", header = T, sep=",")
```

Do some initial plotting of the fakeData
```{r}
library(ggplot2)
p <- ggplot(data=fakeData,
            mapping = aes(x=Meditator.or.Nonmeditator, 
                          y = Ideal.LAP.words))
p + geom_boxplot() #+
#  geom_errorbar(ymin) #?
```



### ANCOVA
Is this the idea?
Ideal Affect response ~ Meditator / Nonmeditator + age (covariant)
```{r}
# Analysis of Covariance 
fit <- aov(Ideal.LAP.words ~ Meditator.or.Nonmeditator + Age, data=fakeData)
fit
```
```{r}
layout(matrix(c(1,2,3,4),2,2))
plot(fit)
```

```{r}
summary(fit)
```

Checking for multiple comparisons.
```{r}
TukeyHSD(fit)
```
I want to replicate Figure 1 here.
```{r}
library(dplyr)
# Need to make it a tibble first?
fakeData2 <- as_tibble(fakeData)

fakeData2$Ideal.LAP.words <- as.numeric(fakeData2$Ideal.LAP.words)

avgMlap <- fakeData2%>%
  group_by(Meditator.or.Nonmeditator)%>%
  summarise(Mean=mean(avgMlap)) # This is returning the following error: argument is not numeric or logical: returning NAargument is not numeric or logical: returning NA. Not sure how to fix it.

p <- ggplot(data=fakeData,
            mapping = aes(x=Meditator.or.Nonmeditator,
                          y=mean(Ideal.LAP.words)))
p + geom_bar(aes(fill=Meditator.or.Nonmeditator,
                 stat = "y"))
```

Am I doing ANCOVA correctly? Here is an explicity ancova command version.
```{r}
library(HH)
ancova <- ancova(Ideal.LAP.words ~ Meditator.or.Nonmeditator + Age, data=fakeData)
ancova
```

```{r}
summary(ancova) # This looks the same so I think what I get from this is the nice looking plot, above?
```

Try controlling for multiple things at once:
```{r}
fit <- aov(Ideal.LAP.words ~ Meditator.or.Nonmeditator + Age + Ideal.HAP.words, data=fakeData) # I think it would actually be Actual.LAP.words not Ideal.HAP.words but still, this seems to work.
fit
```
```{r}
summary(fit)
```

## Here is a go with the fake Piot Data (5 subjects)
### Import the data.
```{r}
library(forcats)
library(tidyverse)
library(dplyr)
library(tidyr)
pilotData <- read_csv(file="~/Desktop/Test2.csv", col_names = T, col_types = NULL, na = c("", "NA"))
pilot <- slice(pilotData, 2:6) # Removing introductory rows
```

### Prepare the data.
We need:
calm + peaceful = LAP
enthusiastic + euphoric = HAP
dull + sleepy = LAN (not used)
hostile + worried = HAN (not used)
```{r}
# Change the relevant columns into numeric values.
# Ideal
pilot$I_peaceful <- as.numeric(pilot$I_peaceful)
pilot$I_calm <- as.numeric(pilot$I_calm)
pilot$I_enthusiastic <- as.numeric(pilot$I_enthusiastic)
pilot$I_euphoric <- as.numeric(pilot$I_euphoric)

# Actual
pilot$A_peaceful <- as.numeric(pilot$A_peaceful)
pilot$A_calm <- as.numeric(pilot$A_calm)
pilot$A_enthusiastic <- as.numeric(pilot$A_enthusiastic)
pilot$A_euphoric <- as.numeric(pilot$A_euphoric)
```

```{r}
# Now find the relevant means to use for plotting and ANCOVA. Group_by "Meditator"
IdealLAP <- group_by(pilot, Meditator)
IdealLAP <- summarize(IdealLAP, avg = mean(I_calm+I_peaceful)/2, sd = sd(I_calm+I_peaceful))

IdealHAP <- group_by(pilot, Meditator)
IdealHAP <- summarize(IdealHAP, avg = mean(I_enthusiastic+I_euphoric)/2)
```

```{r}
# Need to adjust Age (+17 to each value) because Qualtrics listed the order of the answer options rather than the selected value.
pilot$Age <- as.numeric(pilot$Age)
pilot$Age <- pilot$Age + 17
```

### Now for the ANCOVA
This section is not complete yet: I got the Ideal LAP Ratings to gather so that I could run the ANCOVA (below) but ultimately I need to add another covariate (Actual Affect - which I would call something like ActualLAPRating). But when I run more than one gather, the latest one overwrites the previous one. So for now, I only have one covariate, Age.
```{r}
# I think I still need to gather relevant Ideal and Actual groups in pilot so that I have a single variable to point to in my ANCOVA.
gathered_pilot <- gather(pilot, 
                         key = "IdealLAPword", 
                         value = "IdealLAPRating", 
                         I_calm,
                         I_peaceful)
# gathered_pilot <- gather(pilot, 
#                          key = "IdealHAPword", 
#                          value = "IdealHAPRating", 
#                          I_euphoric,
#                          I_enthusiastic)
# gathered_pilot <- gather(pilot, 
#                          key = "ActualLAPword", 
#                          value = "ActualLAPRating", 
#                          A_calm,
#                          A_peaceful)
# gathered_pilot <- gather(pilot, 
#                          key = "ActualHLAPword", 
#                          value = "ActualHAPRating", 
#                          A_euphoric,
#                          A_enthusiastic)
```


```{r}
# Analysis of Covariance 
fit <- aov(IdealLAPRating ~ Meditator + Age, data=gathered_pilot)
fit
```

```{r}
layout(matrix(c(1,2,3,4),2,2))
plot(fit)
```

```{r}
summary(fit)
```

### Plotting Figure 1 from the paper (just the key finding - upper left side).
```{r}
library(ggplot2)
p <- ggplot(data=IdealLAP,
            mapping = aes(x=Meditator, 
                          y = avg))
p + geom_col(aes(fill = Meditator))+
  xlab("Meditators or Nonmeditators")+ # Would still like to remove the "1" and "2" on the x axis.
  ylab("Average Ideal LAP Word Rating")+
  ggtitle("Figure 1. Group Differences Emerge in Ideal LAP Affect (Study 1).")+
  scale_fill_discrete(name = "",
                      breaks=c("1","2"),
                      labels = c("Meditators", "Nonmeditators"))+
  theme_minimal()+
  geom_errorbar(aes(ymin=avg-sd, ymax=avg+sd), # I'm not sure that I want standard deviation here.
                width=.2,                   
                position=position_dodge(.9))
 
```

